---
title: "The Main Title of this paper"
subtitle: "A Custom Project For XYZ Research"
author: "Your Name Here"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 5
    keep_tex: yes
    latex_engine: xelatex
    template: ../latex-template.tex
---

This is the template for a producing a long form paper or article. This text will go below the title and above
the first section heading.

Top-Level Section Heading
================

The formatting is done in Markdown.

You can write LaTeX: $\LaTeX \sum_1^pi a^2$

And you can write full equations using the double-dollar sign notation:

$$ \alpha \subset \beta + \Sigma + \frac{pi = 3.14152}{\text{eleven}} $$

Second-level heading
---------

Here is how to create a hierarchy of sections within your paper.

Embedding R Code
-----------

You can calculate numbers on the fly $2+3$ = `r 2+3`.

Use the `knitr::kable` function in an `asis` block to make nice tables:

```{r toprows}
knitr::kable(head(cars))
```

And use markup to make plain-text show up in a nice box:

```{r summary, results='markup'}
print(summary(cars))
```

```{r plotting, message=FALSE}
plot(cars)
```

